Proposed Solution

### 2016-05-08 CAV/evaluation.tex

\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
By using language extensions (FlexibleInstances and MultiParamTypeClasses), this typeclass can be made polymorphic over the data structure as denoted by \lstinline{Foldable t =>}.
The user can then choose a data structure that is most natural to the rule they are implementing.
For example, in our implementation, Missing Entries were easier to manipulate in lists, while Type Errors fit more naturally into a hashmap.
This typeclass defines the three functions that each set of rules must implement to work with our system.
Typeclasses and other features of Haskell means that our system consists of only 267 lines of code, with another 233 for the rule modules.
With an average size of 58 lines of code for each rule module, this is evidence of how simple it is to extend \app with new rules.

@@

@@

We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb).
In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of a ordering error.
This is a result of our context embedding in the translation to the intermediate representation - reordering the value puts it in a new context where the type is now also incorrect.

>>>>

\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
By using language extensions (FlexibleInstances and MultiParamTypeClasses), this typeclass can be made polymorphic over the data structure as denoted by \lstinline{Foldable t =>}.
The user can then choose a data structure that is most natural to the rule they are implementing.
For example, in our implementation, Missing Entries were easier to manipulate in lists, while Type Errors fit more naturally into a hashmap.
This typeclass defines the three functions that each set of rules must implement to work with our system. The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.

Typeclasses and other features of Haskell means that our system consists of only 267 lines of code, with another 233 for the rule modules.
With an average size of 58 lines of code for each rule module, this is evidence of how simple it is to extend \app with new rules.

@@

The tool is available for download at \url{marksantolucito.com/cavae.html}.

@@

We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb).
In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of an ordering error.
This is a result of our context embedding in the translation to the intermediate representation - reordering the value puts it in a new context where the type is now also incorrect.

### 2016-05-08 CAV/related.tex

\section{Conclusion}

In this paper, we introduce \app, a highly modular framework 
that allows verification of configuration files, 
even without a language model of the file.
New verification properties require only a small amount of code 
and are not language specific, 
all indicating that \app could be widely adopted by system administrators.
Such a verification tool that scales in both performance and expressivity 
can revolutionize configuration file checking, 
reducing the cost of system maintenance and failure dramatically.

>>>>

\section{Conclusions}

In this paper, we introduce \app, a highly-modular framework that allows verification of configuration files, even without a language model of the file.
New verification properties require only a small amount of code and are not language specific, all indicating that \app could be widely adopted by system administrators.
Such a verification tool that scales in both performance and expressivity can revolutionize configuration file checking, reducing the cost of system maintenance and failure dramatically.

The field of verification must guarantee the reliability entire systems, and 31\% of all system failures are caused by misconfiguration, while only 20\% are caused by program bugs ~\cite{xu13do}. We hope \app can be  a catalyst to spark interest in the potential impact of verification for configuration files.
